Measuring matter effects in Neutron star - Black hole binaries with Advanced LIGO

### 2016-02-02 Paper/paper.tex
changes to paper

@@

while (ii) the same for the other $3$ less constrained parameters rails against

@@

\begin{enumerate}
\item Above what SNR values, below what mass-ratios, above what BH spins, etc, 
do we begin to care about NS deformability?\newline
``one interesting plot to make would be the parameter bias (max-Likelihood
parameters minus true parameters) vs SNR, as functionals of q/sBH/Lambda, when
using T signals recovered with N templates.''\newline
`` another interesting plot to make would be the fitting-factors recovered with
a discrete (search oriented) template bank of BBH waveforms, for NSBH signals of
loudness, deformability, spins, mass-ratios, etc. Which parameter plays the 
dominant role in paramter regions where the bank does not suffice to recover
the desired threshold of optimal SNR?''
\end{enumerate}

>>>>

\begin{enumerate}
\item Above what SNR values, below what mass-ratios, above what BH spins, etc, 
do we begin to care about NS deformability?\newline
``one interesting plot to make would be the parameter bias (max-Likelihood
parameters minus true parameters) vs SNR, as functionals of q/sBH/Lambda, when
using T signals recovered with N templates.''\newline
\end{enumerate}

@@

while (ii) the other $3$ less constrained parameters rail against

@@
